sem

### 2023-02-07 scripts/workshop/sem.Rmd
minor edit
Update sem.Rmd

```{r, message = F}
library(here)

library(tidyverse)
library(magrittr)
library(piecewiseSEM)
library(nlme)
library(lmerTest)
library(mgcv)
library(dagitty)
```

@@

>>>>

```{r, message = F}
library(here)
library(tidyverse)
library(magrittr)
library(piecewiseSEM)
library(nlme)
library(lmerTest)
library(mgcv)
library(dagitty)
```

@@

Example with GAMs from Lefcheck textbook: https://jslefche.github.io/sem_book/local-estimation.html#extensions-to-non-linear-models

```{r}
set.seed(100)
n <- 100
x1 <- rchisq(n, 7)
mu2 <- 10*x1/(5 + x1)
x2 <- rnorm(n, mu2, 1)
x2[x2 <= 0] <- 0.1
x3 <- rpois(n, lambda = (0.5*x2))
x4 <- rpois(n, lambda = (0.5*x2))
p.x5 <- exp(-0.5*x3 + 0.5*x4)/(1 + exp(-0.5*x3 + 0.5*x4))
x5 <- rbinom(n, size = 1, prob = p.x5)
dat2 <- data.frame(x1 = x1, x2 = x2, x3 = x3, x4 = x4, x5 = x5)
```

```{r}
shipley_psem2 <- psem(
  lm(x2 ~ x1, data = dat2),
  lm(x3 ~ x2, data = dat2),
  lm(x4 ~ x2, data = dat2),
  lm(x5 ~ x3 + x4, data = dat2)
)

#LLchisq(shipley_psem2)
```

m1 <- gam(x2 ~ s(x1), data = dat2, family = gaussian)
m2 <- glm(x3 ~ x2, data = dat2, family = poisson)
m3 <- gam(x4 ~ x2, data = dat2, family = poisson)
m4 <- glm(x5 ~ x3 + x4, data = dat2, family = binomial)

shipley_psem3 <- psem(m1, m2, m3, m4)

#LLchisq(shipley_psem3)
```
